Cytoplasm Simulation

### 2019-09-12 paper/virtual_cytoplasm_v2.tex
Makefile, manuscript update

\subsubsection{Aggregation}
We observed aggregation of the metabolites that contain phosphate, ATP and FBP, with Mg2+ that was used as initially used as counter-ion for ATP and tRNA. After running simulations of small boxes containing just these metabolites and Mg2+, we found that completely protonating their phosphate groups can prevent aggregation. Thus, we advise caution when dealing with small molecules that are highly charged, such as ATP and FBP. Trial simulations with small boxes in which these metabolites are in high concentration to verify if they'll aggregate with Mg2+ or other charged species that are present in the box. In the specific case of ATP and FBP modeled with GAFF in boxes containing Mg2+, we advise that they should be completely protonated even though that is not their physiological protonation state.

>>>>

\begin{figure}
\includegraphics[scale=0.6]{msd.pdf}
\caption{Diffusion coefficient of crowders from single molecule simulations (blue bars) and cytoplasm simulations (orange bars).}
\end{figure}

\begin{figure}
\includegraphics[scale=0.6]{diff_cyto_over_singles.pdf}
\caption{The ratio between diffusion coefficient obtained from cytoplasm to single molecule simulations. The crowders are sorted according to their sizes on the x-axis.}
\end{figure}

\begin{figure}
\includegraphics[scale=0.6]{rmsd.pdf}
\caption{Root mean squared displacement (rmsd) for 8 proteins from single molecule simulation (blue bars) and cytoplasm simulation (orange bars). The average rmsd for each protein in single molecule simulation is over number of chains of proteins and three replica. The average rmsd for each protein in cytoplasm simulation are over number of chains of proteins, number of appearance and three replica. The error bars show the standard errors.}
\end{figure}

\begin{figure}
\includegraphics[scale=0.6]{sasa.pdf}
\caption{Solvent accessible surface area (sasa) for 8 proteins from single molecule simulation (blue bars) and cytoplasm simulation (orange bars). The average sasa for each protein in single molecule simulation is over number of chains of proteins and three replica. The average sasa for each protein in cytoplasm simulation are over number of chains of proteins, number of appearance and three replica. The error bars show the standard errors.}

\end{figure}

\begin{figure}
\includegraphics[scale=0.6]{rmsf.pdf}
\caption{Root mean squared fluctuations (rmsf) for 8 crowders from single molecule simulation (blue bars) and cytoplasm simulation (orange bars). x-axis shows the residues for each chain of proteins. The average rmsf for each protein in single molecule simulation is over number of chains of proteins and three replica. The average rmsd for each protein in cytoplasm simulation are over number of chains of proteins, number of appearance and three replica. The error bars show the standard errors.}
\end{figure}

\subsubsection{Oligomers under crowded condition}
\begin{figure}
\includegraphics[scale=0.6]{hb.pdf}
\caption{Intramolecular hydrogen bonds (hb) for oligomers from single molecule simulation (blue bars) and cytoplasm simulation (orange bars). The average hydrogen bonds for each oligomer in single molecule simulation is over three replica. The average hydrogen bonds for each oligomer in cytoplasm simulation is over number of appearance of the oligomer in three replica. The error bars show the standard errors.}
\end{figure}

\subsubsection{Aggregation}
We observed aggregation of the metabolites that contain phosphate, ATP and FBP, with Mg2+ that was used as initially used as counter-ion for ATP and tRNA. After running simulations of small boxes containing just these metabolites and Mg2+, we found that completely protonating their phosphate groups can prevent aggregation. Thus, we advise caution when dealing with small molecules that are highly charged, such as ATP and FBP. Trial simulations with small boxes in which these metabolites are in high concentration to verify if they'll aggregate with Mg2+ or other charged species that are present in the box. In the specific case of ATP and FBP modeled with GAFF in boxes containing Mg2+, we advise that they should be completely protonated even though that is not their physiological protonation state. The topology and structure files we are providing for ATP and FBP on github are already protonated.
